---
title: "Cervical Dystonia RCT data codebook"
author: "Peter Higgins"
date: "10/18/2020"
output: 
  html_document:
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flextable)
```


## Cervical Dystonia Dataset Codebook

Source: <br>
This data set is from a study published in 1999 in the journal Neurology,

A. Brashear, M.F. Lew, D.D. Dykstra, C.L. Comella, S.A. Factor, R.L. Rodnitzky, R. Trosch, C. Singer, M.F. Brin, J.J. Murray, J.D. Wallace, A. Willmer–Hulme, M. Koller (1999), Safety and efficacy of NeuroBloc (botulinum toxin type B) in type A–responsive cervical dystonia. Neurology, 53(7), 1439.

This dataset has been passed through Statistical Methods for the Analysis of Repeated Measurements by Charles S. Davis, pp. 161-163 (Springer, 2002) and can also be found at Frank Harrell's website here.

### Codebook

```{r, echo=FALSE, message=FALSE}
cdystonia_codebook <- tribble(
  ~variable, ~position, ~Variable_Label, ~units, ~Codes, ~type,
  "week", 1, "Week of Observation, 0-16", NA, NA, "numeric",
  "site", 2, "Study Site, 1-9", NA, NA, "double",
  "id", 3, "patient id at each site (not unique across sites); 1-19", NA , NA, "numeric",
  "treat", 4, "treatment assignment with levels: 1 = placebo, 2 = BotB5000, 3 = BotB10000", NA, NA, "double",
  "age", 5, "Age", "years", NA, "numeric",
  "sex", 6, "sex of participant, 1 = F, 2 = M", NA, NA, "double",
  "twstrs", 7, "total score of Toronto Western Spasmodic Torticollis Rating Scale, range 0-87", NA, NA, "numeric"
) %>% 
  flextable() %>% 
  fontsize(size = 11) %>% 
  width(width = c(1, 0.5, 2, 0.5, 1.25, 0.5))
cdystonia_codebook
```