---
output: 
  html_document:
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flextable)
```

## Indomethacin RCT to prevent PEP Dataset Codebook

Source: This data set is provided by B. Joseph Elmunzer, the lead author on this randomized controlled trial. This trial was published in the New England Journal of Medicine in 2012, volume 366, pages 1414-1422. The article is accessible at [_A Randomized Trial of Rectal Indomethacin to Prevent Post-ERCP Pancreatitis_](https://www.nejm.org/doi/full/10.1056/NEJMoa1111103)

This data set is anonymized with invented study ids for each participant.

## Codebook

```{r, echo=FALSE, message=FALSE}
indo_rct_codebook <- tribble(
  ~variable, ~position, ~Var_Label, ~units, ~Codes, ~type,
  "id", 1, "Participant ID", NA, "1001-4003", "numeric",
  "site", 2, "Study Site (center)", NA, "1 = University of Michigan, 2= Indiana University, 3 = University of Kentucky, 4 = Case Western", "factor",
  "age", 3, "Age in Years", "years", "18-90", "numeric",
  "risk", 4, "post hoc risk score", "points", NA, "numeric",
  "gender", 5, "Gender", NA, "1_female, 2_male", "factor",
  "sod", 6, "sphincter of oddi dysfunction was present, a risk factor favoring post-ERCP pancreatitis", NA, "0_no, 1_yes", "factor",
  "pep", 7, "previous post-ERCP pancreatitis (PEP), a risk factor for future PEP", NA, "0_no, 1_yes", "factor",
  "recpanc", 8, "Recurrent Pancreatitis, a risk factor for future PEP", NA, "0_no, 1_yes", "factor",
  "psphinc", 9, "a Pancreatic Sphincterotomy was performed, a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "precut", 10, "a sphincter pre-cut was needed to enter the papilla, a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "difcan", 11, "Cannulation of the papilla was difficult, a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "pneudil", 12, "Pneumatic dilation of the papilla was performed, a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "amp", 13, "An Ampullectomy was performed for dysplasia or cancer, which could be a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "paninj", 14, "Contrast was injected into the pancreas during the procedure, a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "acinar", 15, "The pancreas appeared to have acinarization on imaging, which could be a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "brush", 16, "Brushings were taken from the pancreatic duct, a possible risk factor favoring post-ERCP pancreatitis", NA, "0_no, 1_yes", "factor",
  "asa81", 17, "Aspirin was used at a dose of 81 mg per day, which may increase the risk of bleeding", NA, "0_no, 1_yes", "factor",
  "asa325", 18, "Aspirin was used at a dose of 325 mg per day, which may increase the risk of bleeding", NA, "0_no, 1_yes", "factor",
  "asa", 19, "Aspirin was used at any dose, which may increase the risk of bleeding", NA, "0_no, 1_yes", "factor",
  "prophystent", 20, "A pancreatic duct stent was placed at the end of the procedure per the judgement of the endoscopist (more often in high-risk cases), a potential protective effect against PEP", NA, "0_no, 1_yes", "factor",
  "therastent", 21, "A pancreatic duct stent was placed in order to treat a clinically significant narrowing of the pancreatic duct, a potential protective effect against PEP", NA, "0_no, 1_yes", "factor",
  "pdstent", 22, "A pancreatic duct stent was placed at the end of the procedure for any reason, a potential protective effect against PEP", NA, "0_no, 1_yes", "factor",
  "sodsom", 23, "Sphincter of oddi manometry was performed during the procedure for SOD, a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "bsphinc", 24, "A biliary sphincterotomy was performed, which could be a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "bstent", 25, "A biliary stent was placed to relieve significant biliary obstruction", NA, "0_no, 1_yes", "factor",
  "chole", 26, "Choledocholithiasis (gallstones blocking the biliary duct) was present", NA, "0_no, 1_yes", "factor",
  "pbmal", 27, "Malignancy of the biliary duct or pancreas was found", NA, "0_no, 1_yes", "factor",
  "train", 28, "A trainee participated in the ERCP, which could be a risk factor for PEP", NA, "0_no, 1_yes", "factor",
  "outcome", 29, "outcome of post-ercp pancreatitis", NA, "0_no, 1_yes", "factor",
  "status", 30, "outpatient status", NA, "0_no, 1_yes", "factor",
  "type", 31, "Sphincter of Oddi dysfunction type/level - higher numbers are more severe with greater association with PEP", NA, "0_no SOD, 1_type 1, 2_type 2, 3_type 3", "factor",
  "rx", 32, "treatment arm", NA, "0_placebo, 1_indomethacin", "factor",
  "bleed", 33, "A gastrointestinal bleed occurred (which could be a complication of indomethacin therapy)", NA, "1 = no, 2 = yes, NA = not recorded", "numeric"
  
) %>% 
  flextable() %>% 
  fontsize(size = 11) 
#%>% 
 # width(width = c(1, 0.25, 4, 0.75, 1.25, 1))

indo_rct_codebook

```




