---
title: "Indomethacin data codebook"
author: "Peter Higgins"
date: "7/24/2021"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flextable)
```


## Indomethacin Dataset Codebook

Source: This data set is from a pharmacokinetic study of intravenous dosing of the anti-inflammatory and pain relieving medication, indomethacin, in 6 subjects, published in 1976 in the Journal of Pharmacokinetics and Biopharmaceutics.
 
 Kwan, Breault, Umbenhauer, McMahon and Duggan (1976) Kinetics of Indomethacin absorption, elimination, and enterohepatic circulation in man. Pharmacokinetics and Biopharmaceutics. 1976 Jun;4(3):255-80.  doi: 10.1007/BF01063617.

This dataset is is one of the core datasets in base R. It can be used for examples of line plots over time, grouped by subject, and non-linear modeling, including general additive models (GAMs).

### Codebook

```{r, echo=FALSE, message=FALSE}
indometh_codebook <- tribble(
  ~variable, ~position, ~Variable_Label, ~units, ~Codes, ~type,
  "subject", 1, "Subject ID", NA, NA, "character",
  "time", 2, "Time of plasma sampling", "hours", NA, "double",
  "conc", 3, "Concentration of Indomethacin in the plasma", "mcg/mL", NA, "double"
) %>% 
  flextable() %>% 
  fontsize(size = 11) %>% 
  width(width = c(1, 0.5, 2, 0.5, 1.25, 0.5))
indometh_codebook
```
