---
title: "Polyps data codebook"
author: "Peter Higgins"
date: "10/18/2020"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flextable)
```


## Polyps Dataset Codebook

Source: This data set is from a study published in 1993 in the New England Journal of Medicine,
 
 F. M. Giardiello, S. R. Hamilton, A. J. Krush, S. Piantadosi, L. M. Hylind, P. Celano, S. V. Booker, C. R. Robinson and G. J. A. Offerhaus (1993), Treatment of colonic and rectal adenomas with sulindac in familial adenomatous polyposis. New England Journal of Medicine, 328(18), 1313–1316.
 
This dataset is derived from and improved upon from polyps and polyps3 in the {HSAUR} package, which divides up the dataset to different times, neglects the NAs, and does not include participant IDs. Consulting the original paper was quite helpful in reconstructing this dataset.

### Codebook

```{r, echo=FALSE, message=FALSE}
polyps_codebook <- tribble(
  ~variable, ~position, ~Variable_Label, ~units, ~Codes, ~type,
  "participant_id", 1, "Participant ID", NA, NA, "character",
  "sex", 2, "Sex", NA, "male, female", "factor",
  "age", 3, "Age", "years", NA, "numeric",
  "baseline", 4, "Number of Polyps at Baseline", NA, NA, "numeric",
  "treatment", 5, "Treatment Assigned", NA, "sulindac, placebo", "factor",
  "number3m", 6, "Number of Polyps at 3 Months", NA, NA, "numeric",
  "number12m", 7, "Number of Polyps at 12 Months", NA, NA, "numeric"
) %>% 
  flextable() %>% 
  fontsize(size = 11) %>% 
  width(width = c(1, 0.5, 2, 0.5, 1.25, 0.5))
polyps_codebook
```