---
title: "Streptomycin for Tuberculosis data codebook"
author: "Peter Higgins"
date: "6/24/2021"
output: 
  html_document:
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(flextable)
```


## Streptomycin for Tuberculosis Dataset Codebook

Source: This data set is from a prospective, randomized, placebo-controlled clinical trial, _Streptomycin Treatment of Pulmonary Tuberculosis_  published on October 30, 1948 in the British Medical Journal, pages 769-782, by the Streptomycin in Tuberculosis Trials Committee. This is often considered the first modern randomized clinical trial ever published.

This dataset is reconstructed from the article to the best of my ability, and particularly from tables 1-4, which can be reconstructed exactly with janitor::tabyl(), or a more modern Table 1 can be created with gtsummary::tbl_summary(). The _particpant_id_ variable was added to this reconstructed dataset. The _radnum_ variable and the _improved_ variable were added to allow for multivariate and logistic regression modeling (though you can also use logistic regression for the dichotomous outcome of death, radnum =1). You can read the original study in a the BMJ [here](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2091872/pdf/brmedj03701-0007.pdf).

### Codebook

```{r, echo=FALSE, message=FALSE}
strep_tb_codebook <- tribble(
  ~variable, ~position, ~Variable_Label, ~units, ~Codes, ~type,
  "patient_id", 1, "Participant ID", NA, NA, "character",
  "arm", 2, "Study Arm", NA, "Streptomycin, Control", "factor",
  "dose_strep_g", 3, "Dose of Streptomycin in Grams", "grams", NA, "numeric",
  "dose_PAS_g", 4, "Dose of Para-Amino-Salicylate in Grams", "grams", NA, "numeric",
  "gender", 5, "Gender", NA, "M = Male, F = Female", "factor",
  "baseline_condition", 6, "Condition of the Patient at Baseline", NA, "1_Good, 2_Fair, 3_Poor", "factor",
  "baseline_temp", 7, "Oral Temperature at Baseline", "Degrees F", "1_98-98.9F, 2_99-99.9F, 3_100-100.9F, 4_100F+", "factor",
  "baseline_esr", 8, "Erythrocyte Sedimentation Rate at baseline", "millimeters per hour", "1_1-10, 2_11-20, 3_21-50, 4_51+", "factor",
  "baseline_cavitation", 9, "Cavitation of the Lungs on chest X-ray at baseline", NA, "yes, no", "factor",
  "strep_resistance", 10, "Resistance to Streptomycin at 6m", NA, "1_sens_0-8, 2_mod_8-99, 3_resist_100+", "factor",
  "radiologic_6m", 11, "Radiologic outcome at 6m", NA, "1_Death, 2_Considerable Deterioration, 3_Moderate_deterioration, 4_No_change, 5_Moderate_improvement, 6_Considerable_improvement", "factor",
  "radnum", 12, "Numeric Rating of Chest X-ray at month 6", NA, "1-6", "numeric",
  "improved", 13, "Dichotomous Outcome of Improved", NA, "TRUE, FALSE", "logical",
) %>% 
  flextable() %>% 
  fontsize(size = 11) %>% 
  width(width = c(1, 0.5, 1.25, 1, 1.25, 0.5))

strep_tb_codebook

```

