---
title: "Filtering with Multiple Logical Statements"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(medicaldata)
library(janitor)
knitr::opts_chunk$set(echo = FALSE)
prostate <- medicaldata::blood_storage %>% 
  clean_names() %>% as_tibble()
```


## Filtering with Multiple Logical Statements

We will start with the prostate dataset, and combine multiple logical statements to filteR our Rows.


### Exercise 1

Write the R code required to filter the prostate dataset to rows with **both** a prostate volume (p_vol) greater than 90 AND a tumor volume (t_vol) >2.

```{r ex1, exercise=TRUE, error=TRUE, lines = 5}
prostate %>% 
  select(age, p_vol, t_vol) %>% 
  filter()
```

```{r ex1-hint}
prostate %>% 
  select(age, p_vol, t_vol) %>% 
  filter(p_vol > 90 & t_vol >2)
```

### Exercise 2

Write the R code required to filter the prostate dataset to rows with either a family history (fam_hx) of prostate cancer or a preop_psa >20.

```{r ex2, exercise=TRUE, error=TRUE, lines = 5}
prostate %>% 
  select(age, preop_psa, fam_hx) %>% 
  filter()
```

```{r ex2-hint}
prostate %>% 
  select(age, preop_psa, fam_hx) %>% 
  filter(fam_hx ==1 | preop_psa > 20)

```

### Exercise 3

Write the R code required to filter the prostate dataset to high risk patients who are either African-American (aa), or have a surgical Gleason score (s_gs) of 4, but not both


```{r ex3, exercise=TRUE, error=TRUE, lines = 5}
prostate %>% 
  select(age, aa, s_gs) %>% 
  filter()
```

```{r ex3-hint}
prostate %>% 
  select(age, aa, s_gs) %>% 
  filter(xor(aa ==1, s_gs == 4))
```

### Exercise 4

Write the R code required to filter the prostate dataset to rows with (age >70 OR preop_psa >= 15) AND
**not** African-american.

```{r ex4, exercise=TRUE, error=TRUE, lines = 5}
prostate %>% 
  select(age, preop_psa, aa) %>% 
  filter()
```

```{r ex4-hint}
prostate %>% 
  select(age, preop_psa, aa) %>% 
  filter( (age > 70 | preop_psa >= 15) & aa != 1)
```

