---
title: "Filtering Strings"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(medicaldata)
library(janitor)
knitr::opts_chunk$set(echo = FALSE)

# can comment out the next line so shiny will run,
# but then exercises won't work
covid <- medicaldata::covid_testing 
```


## Filtering Strings

We will start with the covid dataset, and combine multiple logical statements to filteR our Rows.


### Exercise 1

Write the R code required to filter the covid dataset to rows with **both** a fake_first_name of "penny" and a fake_first_name of "targaryen".

```{r ex1, exercise=TRUE, error=TRUE, lines = 5}
covid %>% 
  select(subject_id, fake_first_name, fake_last_name) %>%
  filter(--- & ---)
```

```{r ex1-hint}
covid %>% 
  select(subject_id, fake_first_name, fake_last_name) %>%
  filter(fake_first_name == "penny" & fake_last_name == "targaryen")
```

### Exercise 2

Write the R code required to filter the covid dataset to rows with a payor_group of "government".

```{r ex2, exercise=TRUE, error=TRUE, lines = 5}
covid %>% 
  select(subject_id, patient_class, payor_group) %>% 
  filter()
```

```{r ex2-hint}
covid %>% 
  select(subject_id, patient_class, payor_group) %>% 
  filter(payor_group == "government")
```

### Exercise 3

Write the R code required to filter the covid dataset to subjects who were seen in some part of radiology (includes the string "rad" in the clinic_name variable). Page through the results to check your work.


```{r ex3, exercise=TRUE, error=TRUE, lines = 5}
covid %>% 
  select(study_id, clinic_name) %>% 
  filter(str_detect())
```

```{r ex3-hint}
covid %>% 
  select(subject_id, clinic_name) %>% 
  filter(str_detect(clinic_name, "rad"))
```

### Exercise 4

Write the R code required to filter the covid dataset to subjects who were **NOT** seen in any clinical setting that ends in "ology". Page through the results to check your work.


```{r ex4, exercise=TRUE, error=TRUE, lines = 5}
covid %>% 
  select(subject_id, clinic_name) %>% 
  filter(---)
```

```{r ex4-hint}
covid %>% 
  select(subject_id, clinic_name) %>% 
  filter(!str_detect(clinic_name, "ology"))
```

### Exercise 5

Write the R code required to filter the covid dataset to subjects who were in a patient_class seen by surgery. Page through the results to check your work.


```{r ex5, exercise=TRUE, error=TRUE, lines = 5}
covid %>% 
  select(subject_id, patient_class) %>% 
  filter(---)
```

```{r ex5-hint}
covid %>% 
  select(subject_id, patient_class) %>% 
  filter(str_detect(patient_class, "surgery"))
```
