---
title: "Filtering Dates with Lubridate"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(medicaldata)
library(janitor)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE)

# can comment out the next 2 lines to get this app to run,
# but then exercises 1 and 2 fail
covid_dates <- medicaldata::covid_testing %>%
  mutate(fake_date = lubridate::ymd("2020-03-01") + pan_day)

bmt_dates <- medicaldata::cytomegalovirus %>% 
  clean_names() %>% 
  mutate(fake_dx_date = ymd("2014-01-01") + days(round(runif(1,1,364))),
  fake_bmt_date = fake_dx_date + days(round(time_to_transplant*30)),
  fake_agvhd_date = fake_bmt_date + days(round(time_to_agvhd*30)))

```




## Filtering Dates with Lubridate

We will start with the covid dataset, and filteR for observations on particular dates.

### Exercise 1

Write the R code required to filter the covid_dates dataset to rows with a fake_date of April 7, 2020.

```{r ex1, exercise=TRUE, error=TRUE, lines = 5}
covid_dates %>%
  select(subject_id, fake_date) %>%
  filter(---)
```

```{r ex1-hint, error=TRUE}
covid_dates %>%
  select(subject_id, fake_date) %>%
  filter(fake_date == ymd("2020-04-07"))
```

### Exercise 2

Write the R code required to filter the covid_dates dataset to rows with a fake_date between March 10, 2020, and March 17, 2020.

```{r ex2, exercise=TRUE, error=TRUE, lines = 5}
covid_dates %>%
  select(subject_id, fake_date) %>%
  filter(---)
```

```{r ex2-hint-1, error=TRUE}
covid_dates %>%
  select(subject_id, fake_date) %>%
  filter(between(fake_date, ---, ---)) %>%
  arrange(fake_date)
```

```{r ex2-hint-2, error=TRUE}
covid_dates %>%
  select(subject_id, fake_date) %>%
  filter(between(fake_date, ymd(---), ymd(---))) %>%
  arrange(fake_date)
```

```{r ex2-solution, error=TRUE}
covid_dates %>%
  select(subject_id, fake_date) %>%
  filter(between(fake_date, ymd("2020-03-10"), ymd("2020-03-17"))) %>%
  arrange(fake_date)
```


### Exercise 3

Write the R code required to filter the bmt_dates dataset to rows with a fake_avghd_date after a date two years before June 1, 2020.

```{r ex3, exercise=TRUE, error=TRUE, lines = 5}
bmt_dates %>%
  select(id, fake_agvhd_date) %>%
  filter(---)
```

```{r ex3-hint-1, error=TRUE}
bmt_dates %>%
  select(id, fake_agvhd_date) %>%
  filter(fake_agvhd_date >
           today() -   ---)
```

```{r ex3-solution, error=TRUE}
bmt_dates %>%
  select(id, fake_agvhd_date) %>%
  filter(fake_agvhd_date >
           ymd("2020-06-30") - years(2))
```

### Exercise 4

Write the R code required to filter the bmt_dates dataset to subjects with a fake_bmt_date on a Wednesday (the 4th weekday). You should get 11 observations.


```{r ex4, exercise=TRUE, error=TRUE, lines = 5}
bmt_dates %>%
  select(id, fake_bmt_date) %>%
  filter(---)
```

```{r ex4-hint, error=TRUE}
bmt_dates %>%
  select(id, fake_bmt_date) %>%
  filter(wday(fake_bmt_date) == 4)
```

### Exercise 5

Write the R code required to filter the bmt_dates dataset to subjects who had a bone marrow transplant between January 1, 2017 and December 31, 2020.


```{r ex5, exercise=TRUE, error=TRUE, lines = 5}
bmt_dates %>%
  select(id, fake_bmt_date) %>%
  filter(---) %>%
  arrange(fake_bmt_date)
```

```{r ex5-hint, error=TRUE, lines = 5}
bmt_dates %>%
  select(id, fake_bmt_date) %>%
  filter(---) %>%
  arrange(fake_bmt_date)
```

```{r ex5-solution, error=TRUE}
bmt_dates %>%
  select(id, fake_bmt_date) %>%
  filter(between(fake_bmt_date, ymd("2017-01-01"), ymd("2020-12-31"))) %>%
  arrange(fake_bmt_date)
```
