---
title: "Table Exercises"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(broom)
library(gtsummary)
library(janitor)
library(tidyverse)
library(medicaldata)
library(gt)
knitr::opts_chunk$set(echo = TRUE)

supra <- medicaldata::supraclavicular %>% 
  mutate(gender = factor(gender)) %>% 
  mutate(gender = fct_recode(gender,
        "male" = "1", "female" = "0"))  %>% 
  mutate(group = fct_recode(as.factor(group),
        "Mixture" = "1", "Sequential" = "2")) %>% 
  mutate(bmi_cat6 = case_when(bmi < 18.5 ~ "Underweight",
                    bmi >= 18.5 & bmi <25 ~ "Normal weight",
                    bmi >= 25 & bmi <30 ~ "Overweight",
                    bmi >= 30 & bmi <35 ~ "Obesity Class I",
                    bmi >= 35 & bmi <40 ~ "Obestity Class II",
                    bmi >= 40 ~ "Extreme Obesity Class III"))

blood <- medicaldata::blood_storage %>% 
  mutate(aa = factor(AA)) %>% 
  mutate(aa = fct_recode(aa,
      "Not AA" = "0", 
      "African-American" = "1"))  %>% 
    mutate(fam_hx = factor(FamHx)) %>% 
  mutate(fam_hx = fct_recode(fam_hx,
      "No History" = "0", 
      "Family History of PCa" = "1"))  %>% 
  mutate(rbc_age = factor(RBC.Age.Group)) %>% 
  mutate(rbc_age = fct_recode(rbc_age,
   "Younger" = "1", "Middle" = "2",
   "Older" = "3")) %>% 
  mutate(tumor_vol = factor(TVol)) %>% 
  mutate(tumor_vol= fct_recode(tumor_vol,
     "Low" = "1", "Medium" = "2",
      "Extensive" = "3")) %>% 
  mutate(gleason = factor(bGS)) %>% 
  mutate(gleason= fct_recode(gleason,
     "score 0-6" = "1", "score 7" = "2",
    "score 8-10" = "3")) %>% 
  mutate(recur = factor(Recurrence)) %>% 
  mutate(recur= fct_recode(recur,
     "No Recurrence" = "0", "Tumor Recurred" = "1"))

licorice <- medicaldata::licorice_gargle %>% 
  mutate(gender = factor(preOp_gender)) %>% 
  mutate(gender = fct_recode(gender,
          "Male" = "0", "Female" = "1"))  %>% 
  mutate(smoking = factor(preOp_smoking)) %>% 
  mutate(smoking = fct_recode(smoking,
      "Current" = "1", "Past" = "2",
          "Never" = "3")) %>% 
  mutate(mallampati = factor(preOp_mallampati)) %>% 
  mutate(treat = factor(treat)) %>% 
  mutate(treat= fct_recode(treat,
   "Sugar" = "0", "Licorice" = "1")) 

```


## Data Sets
First, let's introduce our three data sets for today    

The **supraclavicular data set** contains data on 103 subjects undergoing upper extremity procedures and receiving supraclavicular anesthesia. They were randomly assigned to a combination of ropivacaine and mepivacaine or sequential mepivacaine followed by ropivacaine. The primary outcome is time to onset of 4-nerve sensory block.
<br>
<br>

The **licorice gargle data set** contains data on 236 subjects undergoing thoracic surgery  with intubation. They were randomly assigned to a gargle of sugar water vs. licorice before anesthesia. The primary outcome is throat pain at 30 minutest post procedure in the PACU.  <br>
<br>

The **blood storage data set** contains data on 316 subjects after radical prostatectomy who received blood transfusion within 30 days of their surgery and had available PSA follow-up data. The main exposure of interest was the RBC storage duration time. It is suspected that transfusion of older blood causes immunosuppression and could increase cancer recurrence.
<br>
<br>

## Making Summary Tables
Let's work on how to make summary tables with three different packages:

1. {dplyr}
2. {janitor}
3. {gtsummary}.  

## Summarizing with Dplyr
### Simple dyplyr grouping and counting
It is simple to get counts by groups with a familiar friend, the {dplyr) package.     
The main functions you will use are

- _tally()_ counts all rows, like n()
- _count(catvars)_  groups by categorical variable arguments, then counts rows within groups, then ungroups. Essentially, _count()_ combines _group_by()_ and _tally()_ and _ungroup()_ into one function.
- _add_tally()_ combines _mutate()_ and _tally()_ to add an new column, named n, to your dataframe.
- _add_count_ combines _mutate()_ and _count()_ to add a new column to your dataframe.     

Examine the code chunk below to see an example of counts from the **blood** dataset by African-American status, Gleason Score category, and Tumor Volume category. You can page through the results to see how many n are in each category. Adding a tally gives you the total n for your denominator.     
You can edit the code to change the name of the tally column, with the argument `name = "total"`. Give this a try.
You can edit the code to sort the categories in descending order of n, with the argument sort = TRUE (after a comma) in the count function. Give this a try.
```{r blood-dplyr1}
blood %>% 
  count(aa, gleason, tumor_vol) %>% 
  add_tally()
```

### Improvements
You can change the name of the tally column, with the argument `name = "total"`. 
You can also sort the categories in descending order of n, with the argument sort = TRUE (after a comma) in the count function. See the example below
```{r blood-dplyr2}
blood %>% 
  count(aa, gleason, tumor_vol, sort = TRUE) %>% 
  add_tally(name = "Total")
```


#### Your turn with licorice!
Use the licorice data to get counts across several categories:
 grouped by gender, preOp_asa, and smoking.   
 Edit the chunk below to get a table of counts.<br>
 If you want to get fancy, try sorting, and adding a named total column with _tally()_. 

```{r dplyr, exercise = TRUE, exercise.lines = 9}
licorice 


```

```{r dplyr-hint-1}
licorice %>% 
  count(gender)
```

```{r dplyr-hint-2}
licorice %>% 
  count(gender, preOp_asa, smoking)
```

```{r dplyr-hint-3}
licorice %>% 
  count(gender, preOp_asa, smoking, sort = TRUE) %>% 
  add_tally(name = "big_N")
```


#### Your turn with supra!
Use the **supraclavicular** dataset to get counts across several categories:
 grouped by gender and group and bmi_cat6,  
 Edit the chunk below to get a table of counts.<br>
 If you want to get fancy, try sorting, and adding a named total column with _tally()_. 

```{r dplyr-supra, exercise = TRUE, exercise.lines = 9}
supra 


```

```{r dplyr-supra-hint-1}
supra %>% 
  count(gender)
```

```{r dplyr-supra-hint-2}
supra %>% 
  count(gender, group, bmi_cat6)
```

```{r dplyr-supra-hint-3}
supra %>% 
  count(gender, group, bmi_cat6, sort = TRUE) %>% 
  add_tally(name = "Denominator")
```

#### Fancy formatting
If you want to control the format of your tables, you can transform them into formats used by the {gt} or {flextable} packages.<br>
The `gt` package works well in HTML and web formats, and has hundreds of formatting options.<br>
The `flextable` package is a bit more flexible, and includes the ability to output tables to HTML, PDF, MS Word, and Powerpoint. <br>
For either of these packages, you just have to take your output from dplyr (a tibble) and convert it to either gt or flextable formats.
This can be done with piping into:

- gt(), or
- flextable()

and then you can format to your heart's content.

The formatting options for `gt` can be found at https://gt.rstudio.com.
<br>
Here is a starter example
```{r}
supra %>% 
  count(gender, group, bmi_cat6, sort = TRUE) %>% 
  add_tally(name = "Denominator") %>% 
  gt() %>% 
   tab_header(
    title = "Counts by Group",
    subtitle = "From the Supraclavicular Dataset"
  ) %>% 
  tab_options(
   table.background.color = "darkorchid",
   heading.background.color = "yellow"
  ) 

```

<br>
The formatting options for `flextable` can be found at https://davidgohel.github.io/flextable/.
<br>
Here is a starter example
```{r}
supra %>% 
  count(gender, group, bmi_cat6, sort = TRUE) %>% 
  add_tally(name = "Denominator") %>% 
  flextable() %>% 
  autofit() %>% 
  bold(part = "header") %>% 
  fontsize(part = "header", size = 16) %>% 
  fontsize(part = "body", size = 14) %>% 
  align(align = "center", part = "all") %>% 
  #note conditional formatting in rows when n>7, turn column n purple and bold. Could do this for P <0.05, etc.
  color(color = "purple", i =~ n>7, j =~ n) %>% 
  bold(i =~ n>7, j =~ n)
```


## Counting in Tabyls with Janitor
Counts can also be obtained in 2 by 2 tables with the _tabyl_ function from the {janitor} package.      
The 3 main functions of {janitor} include

- _tabyl(catvars)_ which makes tables with 1,2, or 3 variables (when using 3 variables, you end up with a list of tables). Unlike the {base} _table()_ function, _tabyl()_ plays well with tidyverse pipes.
- _clean_names()_ which consistently formats variable names
- _get_dupes()_ which helps you find and deal with duplicate rows

Note that there a lot more handy functions in {janitor}, which can be found here:     
https://sfirke.github.io/janitor/reference/index.html      
<br>
In addition to the basic tabyl, you can _adorn_ your table of counts with _adorn_ functions. These include

- _adorn_percentages()_
- _adorn_ns()_ if you also want Ns
- _adorn_pct_formatting()_ to give you nice looking percentages
- _adorn_totals("rows")_ or _adorn_totals("cols")_ for totals
- _adorn_rounding()_     


Review the example below and its output to see how this works.
```{r}
blood %>% 
  tabyl(gleason, tumor_vol) 
```


### Simple janitor tabyl with percentages
We can make this fancier with percentages, rather than just counts.
See the example below to see how this is done.
```{r}
blood %>% 
  tabyl(aa, tumor_vol) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()
```

#### Your turn with licorice!
Now try this with the licorice dataset, making a table of<br>
gender by smoking.
Add nicely formatted percentages and Ns.
```{r tabyl, exercise = TRUE, exercise.lines = 7}
licorice
```

```{r tabyl-hint}
licorice %>% 
  tabyl(gender, smoking)
```

```{r tabyl-solution}
licorice %>% 
  tabyl(gender, smoking) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()
```
### {janitor} tabyl with Totals and Titles

Here is an example of how to improve a simple 2 x 2 table with the {janitor} package function _tabyl_ by adding totals to rows/columns and titles.

```{r}
supra %>% 
  tabyl(gender, group) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_title(row_name = "Gender", 
              col_name = "Group Assigned",
              placement = "combined")
```

Note that the _adorn_title()_ placement argument can also be "top" - see what this looks like in the chunk below.

```{r}
supra %>% 
  tabyl(gender, group) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_title(row_name = "Gender", 
              col_name = "Group Assigned",
              placement = "top")
```
#### Your turn with **blood**!
Make a nicely titled tabyl with totals and titles from the blood datset, with the variables fam_hx and recur.

```{r tabyl2, exercise = TRUE, exercise.lines = 7}
blood
```

```{r tabyl2-hint}
blood %>% 
  tabyl(fam_hx, recur)
```


```{r tabyl2-solution}
blood %>% 
  tabyl(fam_hx, recur) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_title(row_name = "Family History", 
              col_name = "Tumor Recurrence",
              placement = "top")
```

### {janitor} tabyl with pct, without NAs
Missing data, or NAs, are included as a category by default.
This is a good thing, so that you don't miss the presence of missing data.
But it is problematic if you are trying to do a chi square or fisher exact test.
You can just make the tabyl argument _show_na_ false.
See the code chunk below for an example.

```{r}
blood %>% 
  tabyl(gleason, tumor_vol, show_na = F)
```

### Adding  chi squared test to a janitor tabyl 
 Once the NA values are removed, you can then do a chi squared test.
 Just add one line, as in the code chunk below.<br>
 If you have a lot of low-count (<5) cells, you can also use a fisher exact test with _fisher.test()_
```{r}
blood %>% 
  tabyl(gleason, tumor_vol, show_na = F) %>% 
  chisq.test()
```
 
### Your turn with supra!
Now try this with the supraclavicular data,
with a table of group and gender. <br>
Add a chi-squared test.

```{r chi, exercise = TRUE, exercise.lines = 7}
supra 
```


```{r chi-hint}
supra %>% 
  tabyl(group, gender)
```

```{r chi-solution}
supra %>% 
  tabyl(group, gender) %>% 
  chisq.test()
```

#### A Formatting Note for Tabyls
You can format tabyls with {gt} by just piping into the _gt()_ function, then adding formatting options.<br>
```{r}
supra %>% 
  tabyl(group, gender) %>% 
  gt() %>% 
  tab_header(
    title = "Counts by Group",
    subtitle = "From the Supraclavicular Dataset"
  ) %>% 
  tab_options(
   table.background.color = "goldenrod",
   heading.background.color = "orange"
  ) 
```

<br>
To format a tabyl with {flextable}, you have to undo the tabyl formatting first, so you pipe into _untabyl()_ and then into _flextable()_ and then you can format with flextable options. 

```{r}
supra %>% 
  tabyl(group, gender) %>% 
  untabyl() %>% 
  flextable() %>% 
  autofit() %>% 
  bold(part = "header") %>% 
  fontsize(part = "header", size = 20) %>% 
  fontsize(part = "body", size = 18) %>% 
  align(align = "center", part = "all") %>% 
  # note conditional formatting in rows when n>7, turn column n purple and bold. Could do this for P <0.05, etc.
  # rows denoted by i, columns denoted by j (as in i,j)
  color(color = "green", i =~ male>20, j =~ male) %>% 
  bold(i =~ male>20, j =~ male)
```


## Using {gtsummary} to Count Groups
gtsummary is a relatively new package based on the gt package, but it is optimized for clinical trial tables.

- The _tbl_summary()_ function takes the selected table variables and does an auto-summary.
- The _tbl_regression()_ function does the same for regression tables.

Look at this chunk of code using _tbl_summary()_ and its output.
What does each line of code do?

```{r tbl_sum1}
supra %>% 
  select(gender, bmi, age, group) %>% 
  tbl_summary(by = group) 
```

This is a pretty slick and easy summary.
You can modify parts of the table by modifying the default arguments to _tbl_summary()_, including

- label       specify the variable labels printed in table  
- type        specify the variable type (e.g. continuous, categorical, etc.)
- statistic   change the summary statistics presented  
- digits      number of digits the summary statistics will be rounded to  
- missing     whether to display a row with the number of missing observations 
- sort        change the sorting of categorical levels by frequency
- percent     print column, row, or cell percentages

You can also add to the table by piping into _add_ functions, including

- add_p()           add p-values to the output comparing values across groups   
- add_overall()     add a column with overall summary statistics   
- add_n()           add a column with N (or N missing) for each variable   
- add_stat_label()  add a column showing a label for the summary statistics shown in each row   
- add_q()           add a column of q values to control for multiple comparisons   

There are also several functions to format the _gtsummary()_ table including

- modify_header()         relabel columns in summary table  
- bold_labels()           bold variable labels  
- bold_levels()           bold variable levels  
- italicize_labels()      italicize variable labels  
- italicize_levels()      italicize variable levels  
- bold_p()                bold significant p-values  

Here is a fancier example:
```{r}
licorice %>%
  select(gender, smoking, mallampati, preOp_calcBMI, preOp_age, treat) %>% 
  # build base summary table
  tbl_summary(
    # split table by treatment variable
    by = treat,
    # change variable labels
    label = list(preOp_calcBMI ~ "BMI",
                 preOp_age ~ "Age"),
    # change statistics printed in table
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = list("preOp_age" ~ c(1, 2))
  ) %>%
  # add p-values, report t-test, round large pvalues to two decimal place
  add_p(test = list(preOp_calcBMI ~ "t.test"),
                 pvalue_fun = function(x) style_pvalue(x, digits = 2)) %>%
  # add statistic labels
  add_stat_label() %>%
  # bold variable labels, italicize levels
  bold_labels() %>%
  italicize_levels() %>%
  # bold p-values under a given threshold (default is 0.05)
  bold_p(t = 0.52) %>%
  # include percent in headers
  modify_header(stat_by = "**{level}**, N = {n} ({style_percent(p, symbol = TRUE)})")
```

#### More Formatting
Note that if you want to use the formatting functions of `gt` or `flextable`, these are also options. 
Pipe your result into the functions

- _as_gt()_   OR
- _as_flextable()_

Note - one possible gotcha - if you load the package flextable after the package gtsummary, you will need to specify which version of _as_flextable()_ you want, as each has a function by that name. The easiest way to do this is to use gtsummary::as_flextable() so that R knows which version of the function that you want to use.

#### Your Turn with **blood**!
Now try _gtsummary_ on the  blood data set, using the variables age, aa, tumor_vol, and recur, divided by rbc_age categories, in the exercise below
(Note - don't eliminate rbc_age with your select statement)

```{r tbl_sum2, exercise =TRUE, exercise.lines = 7}
blood 

```

```{r tbl_sum2-hint}
blood %>% 
  select(Age, aa, tumor_vol, rbc_age, recur)
```

```{r tbl_sum2-solution}
blood %>% 
  select(Age, aa, tumor_vol, rbc_age, recur) %>% 
  tbl_summary(by = rbc_age) %>% 
  bold_labels() %>%
  italicize_levels() %>%
  add_p() 
```


#### Adding p values for Comparisons with {gtsummary}

You can add comparative P values easily,
see the chunk below (and its output) for an example.

```{r}
supra %>% 
  select(gender, bmi, age, group) %>% 
  tbl_summary(by = group) %>% 
  add_p()
```

#### Your turn!
Now try this yourself on the blood dataset. 
Add p values for this comparison. <br>
Which predictor variables do you think will be significant?

```{r tbl_sum3, exercise = TRUE, exercise.lines = 9}
blood %>% 
  select(Age, aa, FamHx, recur, rbc_age) %>% 
  tbl_summary(by = recur,
  label = list(aa ~ "African-American",
                FamHx ~ "Family History of Prostate Ca",
               rbc_age ~ "Age of Transfused RBC"))
```

```{r tbl_sum3-solution}
blood %>% 
  select(Age, aa, FamHx, recur, rbc_age) %>% 
  tbl_summary(by = recur,
  label = list(aa ~ "African-American",
                FamHx ~ "Family History of Prostate Ca",
               rbc_age ~ "Age of Transfused RBC")) %>% 
  add_p() %>% 
  bold_p(t = 0.10)
```

#### Your turn with licorice!
Now try this yourself on the **licorice** dataset. 
Add p values for this comparison. <br>
Which predictor variables do you think will be significant?

```{r tbl_sum4, exercise = TRUE, exercise.lines = 9}
licorice  %>% 
  select(gender, smoking, mallampati, treat, preOp_age) %>% 
  tbl_summary(by = treat)
```

```{r tbl_sum4-solution}
licorice  %>% 
  select(gender, smoking, mallampati, treat, preOp_age) %>% 
  tbl_summary(by = treat) %>% 
  add_p() %>% 
  bold_p(t = 0.10)
```

## Regression tables with gtsummary

You can easily summarize a linear regression with the {gtsummary} package function _tbl_regression()_

Review the chunk below for an example.
Longer time to onset of anesthesia (more minutes) is a bad outcome. 
Which variables favor a worse outcome?
Are any significant?

```{r regress, exercise = TRUE, exercise.lines = 7}
supra_model_tbl <- lm(onset_sensory ~ gender + group + midazolam + age + subject + bmi_cat6, 
                      data = supra) %>% 
  tbl_regression() 

supra_model_tbl
```
### Your turn!
Try to summarize in a table this model (in the blood dataset) for recurrence of prostate cancer with _tbl_summary_ from the {gtsummary} package.
Be sure to add the exponentiate = TRUE option to get odds ratios when you use _tbl_summary()_

```{r logistic_blood, exercise = TRUE, exercise.lines = 7}
model_recur_tbl <- glm(Recurrence ~ aa + fam_hx + rbc_age + tumor_vol + gleason,
          data = blood)

model_recur_tbl
```

```{r logistic_blood-hint}
model_recur_tbl <- glm(Recurrence ~ aa + fam_hx + rbc_age + tumor_vol + gleason,
                   data = blood) %>% 
   tbl_regression() 


model_recur_tbl
```

```{r logistic_blood-solution}
model_recur_tbl <- glm(Recurrence ~ aa + fam_hx + rbc_age + tumor_vol + gleason,
                   data = blood) %>% 
   tbl_regression(exponentiate = TRUE) 


model_recur_tbl
```
## Building up side by side tables

You can also combine tables with the _tbl_merge_ function from {gtsummary}
Here is an example of a summary table and a modeling table.

### Quick Summary Table with gtsummary
First, this code chunk makes the summary table. 
```{r}
summ_tbl1 <- licorice %>% 
  select(gender, preOp_age, treat) %>% 
  tbl_summary(missing = "no") %>% 
  add_n()
summ_tbl1
```



### Regression table with gtsummary
Then this code chunk builds the model,
`mod_tbl2`,<br> 
and the _tbl_regression()_ function makes the regression table 
```{r}
mod_tbl2 <- lm(pacu30min_throatPain ~ gender + smoking + mallampati + treat, data = licorice) %>% 
  tbl_regression()
mod_tbl2
```

### Now merge these tables
Then you can merge these and add two tab spanners.

```{r}
tbl_merge(
  list(summ_tbl1, mod_tbl2),
  tab_spanner = c("**Summary Statistics**",
                  "**30 Min Cough Outcome**")
)
```


#### Your turn!
1. Make a summary table from the supra dataset - group, gender, bmi, and age
2. Make a regression summary model from the blood dataset with the outcome of onset_motor, and the predictors group, gender, bmi, age, and fentanyl
3. use _tbl_merge_ and some appropriate spanner text to merge these tables.

```{r final, exercise = TRUE, exercise.lines = 15}
summ_tbl_supra


regress_tbl_supra


merged_tbl_blood

```

```{r final-hint}
summ_tbl_supra <- supra %>% 
  select(group, gender, bmi, age)

regress_tbl_supra <- lm(onset_motor ~ group + gender + bmi + age +fentanyl, data = supra)


merged_tbl_blood <-  tbl_merge(list(summ_tbl_supra, regress_tbl_supra))

```


```{r final-solution}
summ_tbl_supra <- supra %>% 
  select(group, gender, bmi, age) %>% 
  tbl_summary() %>% 
  add_n()
summ_tbl_supra


regress_tbl_supra <- lm(onset_motor ~ group + gender + bmi + age +fentanyl, data = supra) %>% 
  tbl_regression()
regress_tbl_supra

merged_tbl_blood <-  tbl_merge(list(summ_tbl_supra, regress_tbl_supra),
            tab_spanner = c("**Summary Statistics**",
                  "**Onset Motor Outcome**"))
merged_tbl_blood
```

## Final Quizzes

```{r dplyr-quiz-1, echo=FALSE}
quiz(caption = "Dplyr Quiz",
  question("Which function in dplyr counts all the rows?",
    answer("summarise()"),
    answer("mutate()"),
    answer("tally()", correct = TRUE),
    answer("count()")
  ),
  question("Which function in dplyr counts rows by group (then ungroups)?",
    answer("count()", correct = TRUE),
    answer("tally()"),
    answer("filter()"),
    answer("n()")
  ),
    question("Which function in dplyr adds the total number of rows as a variable to your dataframe?",
    answer("add_count()"),
    answer("mutate()"),
    answer("add_tally()", correct = TRUE),
    answer("transmute()")
  ),
  question("Which function in dplyr adds the total number of rows *in each group* as a variable to your dataframe?",
    answer("add_count()", correct = TRUE),
    answer("select()"),
    answer("add_tally()"),
    answer("relocate()")
  )
)
```

```{r janitor-quiz-1, echo=FALSE}
quiz(caption = "Janitor Tabyl Quiz",
  question("Which function in janitor makes tables?",
    answer("clean_names()"),
    answer("get_dupes()"),
    answer("tabyl()", correct = TRUE),
    answer("remove_empty()")
  ),
  question("Which function in janitor adds totals to rows or columns of tabyls?",
    answer("adorn_totals()", correct = TRUE),
    answer("adorn_title()"),
    answer("remove_constant()"),
    answer("round_half_up()")
  ),
    question("Which function in janitor adds percentages to rows in tabyls?",
    answer("tabyl()"),
    answer("adorn_percentages('row')", correct = TRUE),
    answer("adorn_title()"),
    answer("adorn_pct_formatting()")
  ),
  question("Which function in janitor formats percentages to 2 digits?",
    answer("adorn_pct_formatting(digits=2)", correct = TRUE),
    answer("adorn_percentages()"),
    answer("adorn_ns()"),
    answer("adorn_totals('row')")
  )
)
```


```{r gtsummary-quiz-1, echo=FALSE}
quiz(caption = "gtsummary Quiz",
  question("Which function in gtsummary makes summary tables?",
    answer("add_p()"),
    answer("modify_header()"),
    answer("tbl_summary()", correct = TRUE),
    answer("bold_labels()")
  ),
  question("Which function in gtsummary makes regression tables?",
    answer("tbl_regression()", correct = TRUE),
    answer("add_n()"),
    answer("as_gt()"),
    answer("as_flextable()")
  ),
    question("Which argument in gtsummary::tbl_summary lets you compare study arms in columns?",
    answer("italicize_labels()"),
    answer("by = treatment_arm", correct = TRUE),
    answer("statistic = list(all_continuous() ~ '{mean} ({sd})'"),
    answer("bold_p(t = 0.2)")
  ),
  question("Which argument in gtsummary::tbl_summary lets you control the formatting of your data?",
    answer("statistic = list(all_continuous() ~ '{mean} ({sd})',
                     all_categorical() ~ '{n} / {N} ({p}%)'),", correct = TRUE),
    answer("by = treatment_arm"),
    answer("add_stat_label()"),
    answer(" modify_header(stat_by = '**{level}**, N = {n}'")
  )
)
```